%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{workentries}

%---------------------------------------------------------
\workentry
{Senior Software Engineer} % Job title
{Adaptive Enterprise Limited}{http://ael-bd.com} % Organization
{Dhaka, Bangladesh}{https://goo.gl/maps/EV7KoqACFQ42} % Location
{Dec. 2014 - Present} % Date(s)
{
  \begin{workitems} % Description(s) of tasks/responsibilities
    \item {Developed, supervised and currently maintaining more than seven of
    {\href{http://www.napcosecurity.com}{NAPCO Security Technologies}}
    biggest state of the art apps to manage home security, home automation, video cameras on Android and React Native utilizing Socket Programming(TCP and UDP), Serial port communication (NDK)
    , H.264 video decoding, Bluetooth LE(Low Energy), IPC, AIDL, Google Vision api, 
    {\href{https://realm.io}{Realm for Android}}
    etc.}
    \item {Implemented an in-house stock exchange analysis app with seamless UX/UI maintaining the Material Design guidelines with tools like
    {\href{https://github.com/PhilJay/MPAndroidChart}{MPAndroidChart}},
    {\href{https://realm.io}{Realm for Android}.}
    }
    \item {Designed and developing a React Native app, that aggregates several reputated government/non-government banks, to make a secured payment rail in the national 
    e-commerce field under 
    {\href{http://doer.com.bd}{DOER.}}
    }
  \end{workitems}
}

%---------------------------------------------------------
\workentry
{Software Engineer} % Job title
{Cloudwell Limited}{http://www.cloudwell.co} % Organization
{Dhaka, Bangladesh}{https://goo.gl/maps/JSANLPJwnfp} % Location
{Aug. 2013 - Dec. 2014} % Date(s)
    {
      \begin{workitems} % Description(s) of tasks/responsibilities
        \item {Developed easy-to-use Android apps for the startup, facilitating 
        {\href{https://www.paywellonline.com/web_paywell/index.php}{Paywell's Payment infrastructure}} 
        from 
        {\href{https://www.youtube.com/channel/UCf_R7aYkzyn_CGZw4xgkNEA}{Paywell Services app}}
        to in-house applications e.g.
        {\href{https://futurestartup.com/2018/03/13/the-evolution-of-cloudwell-clouldwells-strategy-and-ambition-an-interview-with-anisul-islam-founder-and-ceo-cloudwell/}
        {Paywell Distributor/Dealer/Collector/Territory Officer app.}}
        }
        \item {Provisioned backend developers with Servlet
        {\href{http://php-java-bridge.sourceforge.net/pjb/servlet-programming.php}{+php/Java bridge}}
        {\href{http://www.quartz-scheduler.org}{+Quartz Job Scheduler}}
        , by building an app that acts as tiny sms server for 
        {\href{http://www.teletalk.com.bd/dynamicLayout.jsp?page=40002&menuItem=7006}{TeleTalk REB Bill Payment.}}
        \item Java Desktop application (jdk1.6+JavaFX) that pushes sms utilizing 
        {\href{https://www.silverstreet.com}{SilverStreet sms gateway.}}
        }
        \item {Worked with 
        {\href{http://www.telpo.com.cn}{Telpo}}
        and partially developed Paywell application (with the provided SDK on Embedded-C) on 3 different embedded subsystem POS terminals 
        ({\href{https://www.alibaba.com/product-detail/-Telpo-TPS300-EFT-pos-GPRS_576805259.html}{TPS300}}
         , {\href{https://kmychina.en.made-in-china.com/product/xeyJnSQWglcs/China-GPRS-POS-with-PCI-Pinpad-KMY801B-.html}{KMY801B}}
         , {\href{http://movotek.com/products/pos-terminal-mil300/}{MIL300}}         
        )
        }
      \end{workitems}
    }

%---------------------------------------------------------
  \workentry
    {Software Engineer (Android)} % Job title
    {AnnaNovas IT}{https://annanovas.com} % Organization
    {Dhaka, Bangladesh}{https://goo.gl/maps/aA12F5zMTg42} % Location
    {Oct. 2011 - Jun. 2013} % Date(s)
    {
      \begin{workitems} % Description(s) of tasks/responsibilities
        \item {Built several apps using REST api, sqlite, custom views/controls, Google Maps API (v1), FCM/GCM(then Google C2DM) etc from ground up.}
        \item {Developed 3 inbuilt system apps and the launcher app that executes Linux shell commands for }
        {\href{https://www.polaroid.com/kids-tablet-2}{Polaroid Kids Tablet.}}
      \end{workitems}
    }

\end{workentries}
