%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{projectentries}

%---------------------------------------------------------
  \projectentry 
    {\href{http://www.napcosecurity.com/products/ibridge/}{iBridge}}
    {Android
    +{\href{https://developer.android.com/ndk/}{NDK}}
    +{\href{https://www.geeksforgeeks.org/socket-programming-in-java/}{Socket}}
    +{\href{https://developer.android.com/guide/components/aidl}{AIDL}}
    +{\href{https://searchsecurity.techtarget.com/definition/digest-authentication}{Digest Auth}}
    +{\href{https://developer.android.com/guide/topics/media/}{Streaming H.264}}
    +{\href{https://realm.io/docs/java/0.82.2/}{Realm for Android}}
    +{\href{https://developers.google.com/vision/android/barcodes-overview}{Google Vision api}} }
    {
      \begin{projectitems} % Description(s) bullet points
        \item {NAPCO's state-of-the-art security/access control app for intrusion detection, fire alarms, IoT 
        available in Wireless(local \& remote) and panel-wired IBR-TOUCH tablet versions.}
        \item {Smart 
        {\href{https://www.z-wave.com/shop-z-wave-smart-home-products/smart-hubs-napco-napco-i-bridge-z-wave-controller}{Z-Wave™}}
         device automation of indoor and outdoor lights, dimmers, thermostats, locks with scene creation, triggered events \& scheds.}
        \item {Integrated top branded panel's keypad like 
        {\href{https://www.security.honeywell.com/product-repository/6160v}{ADT®/Honeywell®}}
        , {\href{http://www.dsc.com/index.php?n=products&o=view&id=60}{DSC®}}.}
      \end{projectitems}
    }
    
    \projectentry 
    {\href{https://play.google.com/store/apps/details?id=com.napcosecurity.android.ilock&hl=en}{iLock}}
    {Android
    +{\href{https://developer.android.com/guide/components/aidl}{Bluetooth LE}}}
    {
      \begin{projectitems} % Description(s) bullet points
        \item {NAPCO 
        {\href{http://www.alarmlock.com}{Alarm Lock}}
        division's smartphone 
        {\href{https://developer.android.com/guide/components/aidl}{Bluetooth LE }}
        solution for unlocking(/locking for Canadian market) proprietary 
        {\href{http://www.alarmlock.com}{Trilogy®Networx™ ArchiTech™ Series Designer Access Control Locks }} 
        from android device without the need to carry cumbersome ID cards or keys.}
      \end{projectitems}
    }
    
    
    \projectentry 
    {\href{https://www.youtube.com/watch?v=_UDmZebYkEY}{Virtual Keypad \& StarLink} }
    {Android
    +{\href{http://square.github.io/okhttp/}{OkHttp}}
    +{\href{https://www.geeksforgeeks.org/socket-programming-in-java/}{Socket}}
    +{\href{https://developer.android.com/guide/components/aidl}{AIDL}}}
    {
      \begin{projectitems} % Description(s) bullet points
        \item {\href{https://youtu.be/_UDmZebYkEY?t=24}{\textbf{Virtual Keypad - }}
        Conventional keypad screen and 
        {\href{https://www.youtube.com/watch?v=Y1s-n1bF5G4}{keypad-programming }}
        for renowned security keypad manufacturer e.g. 
        {\href{https://www.security.honeywell.com/product-repository/6160v}{ADT®/Honeywell®}}
        , {\href{http://www.dsc.com/index.php?n=products&o=view&id=60}{DSC®}}.}
        \item {\href{https://youtu.be/_UDmZebYkEY?t=70}{\textbf{StarLink - }}
        Universal intrusion alarm reporting mobile solution with Arming/Disarming capabilities on panels.}
      \end{projectitems}
    }

    \projectentry 
    {\href{https://www.polaroid.com/kids-tablet-2}{Polaroid Kids Tablet 2}} 
    {Android with custom UI controllers
    +{\href{https://developer.android.com/guide/topics/media/}{Media api}}}
    {
      \begin{projectitems} % Description(s) bullet 
        \item {\href{https://youtu.be/7bRafa1btPA?t=94}{\textbf{Kids Vids -}} 
        Proprietary app with age control that streams kids friendly videos from YouTube.}
        \item {\href{https://youtu.be/7bRafa1btPA?t=7}{\textbf{Kids Start -}} 
        The Launcher app of the tablet with a feature of restricting apps.}
        \item {\href{https://youtu.be/7bRafa1btPA?t=120}{\textbf{Kids Cam -}} 
        Proprietary app for taking picture and shooting video with built-in fun filters.}
        \item {\href{https://youtu.be/7bRafa1btPA?t=146}{\textbf{Music Player -}} 
        Audio player app with custom visualizer.}
        \item {\href{https://youtu.be/7bRafa1btPA?t=146}{\textbf{DJ Studio -}} 
        A little DJ app for kids with fun sounds and beats.}
        \item {\href{https://www.androidauthority.com/polaroid-kids-tablet-149-99-144498/}{Best design and innovation award winner of CES2013.}
        Featured in
        {\href{https://www.engadget.com/2013/11/06/polaroid-kids-tablet-2/}{Engadget}, }
        {\href{https://www.usatoday.com/story/dispatches/2013/12/17/family-travel-gifts/4038309/}{USA TODAY}, }
        {\href{https://www.youtube.com/watch?v=WqLu0ru4xO8}{Digital Trends}.}
        }
      \end{projectitems}
    }

    \projectentry 
    {\href{https://play.google.com/store/apps/details?id=com.cloudwell.paywell.services}{Paywell Services}} 
    {Android+{\href{https://github.com/bumptech/glide}{Glide}}}
    {
      \begin{projectitems} % Description(s) bullet points
        \item {Designed for retailers or store owners that want to sell mobile airtime and various utility bills of Bangladesh.}
        \item {In-house Distributor, Dealer, Collector, Territory Officer 
        apps satisfying significant aspects of 
        {\href{https://futurestartup.com/2018/03/13/the-evolution-of-cloudwell-clouldwells-strategy-and-ambition-an-interview-with-anisul-islam-founder-and-ceo-cloudwell/}
        {Paywell's bussiness model.}}}
      \end{projectitems}
    }

    \projectentry 
    {Android Development} 
    {{\href{https://developers.google.com/maps/documentation/android-sdk/start}{Google Maps api}}
    +{\href{https://firebase.google.com}{Firebase}}
    +{\href{https://www.instagram.com/developer/}{Instagram api}}
    +{\href{http://square.github.io/okhttp/}{OkHttp}}
    +{\href{https://developer.android.com/guide/topics/media/}{Media Api}}
    +{\href{https://realm.io/docs/java/latest/}{Realm for Android}}
    +{\href{https://github.com/PhilJay/MPAndroidChart}{MPAndroidChart}}}
    {
      \begin{projectitems} % Description(s) bullet points
        \item {{\href{https://play.google.com/store/apps/details?id=com.orba.OneOrchard}{\textbf{OneOrchard - }}}
        OneOrchard brings you a whole different online experience as you use the app along 
        {\href{http://www.orchardroad.org/}{Orchard Road, Singapore.}}}
        \item {{\href{https://annanovas.com/portfolio/beer-prices-android/}{\textbf{Beer Price - }}}
        Get updated prices, selections, locations and rating from over 3,000 bars in Scandinavia. Both price and selection can easily be 
        updated thorugh the in-app report function.}  
        \item {{\href{https://play.google.com/store/apps/details?id=com.SingaporeChineseOrchestra.SCO}{\textbf{Singapore Chinese Orchestra (SCO) - }}}
        Official app for 
        {\href{https://www.sco.com.sg}{Singapore’s only professional Chinese orchestra.}}}  
        \item {{\href{https://annanovas.com/portfolio/my-collection/}{\textbf{My Collection - }}}
        Develop for the people who has great passions on regarding there collected Coin, Stamps and Sports Cards.}  
        \item {{\href{https://play.google.com/store/apps/details?id=com.napco.uidealer.myiseevideo}{\textbf{MyiSeeVideo - }}}
        iSeeVideo app for Napco's video services for 
        {\href{http://www.napcosecurity.com/products/isee-ivr250/}{ISEE series cameras.}}}  
        % \item {{\href{https://futurestartup.com/2018/03/13/the-evolution-of-cloudwell-clouldwells-strategy-and-ambition-an-interview-with-anisul-islam-founder-and-ceo-cloudwell/}
        % {\textbf{Paywell Distributor, Dealer, Collector, Mobile airtime, Territory Officer (In-house) - }}}
        % 5 apps satisfying significant aspects of Paywell's bussiness model, distributor-to-dealer-to-retailer, mobile territory manager.}  
        \item {{\href{https://drive.google.com/file/d/1AE3tdaTBA1hnKjhM2Quv4poWi6oQthwy/view?usp=sharing}{\textbf{CSE (In-house) - }}}
        {\href{https://www.cse.com.bd/}{Chittagong Stock Exchange }}
        analysis app with animated Line chart and Bar chart.}  
        \item {{\href{https://www.akij.net/}{\textbf{Akij BR (In-house) - }}}
        App for sales officers of country's giant 
        {\href{https://www.akij.net}{Akij Group}}
        , to daily market survey and report/generate pdf their fulfilled target to a central server.}  
      \end{projectitems}
    }
    

    \projectentry 
    {React Native Development} 
    {{\href{https://css-tricks.com/snippets/css/a-guide-to-flexbox/}{Flexbox}}
    +{\href{https://redux.js.org/basics/usagewithreact}{Redux}}
    +{\href{https://redux.js.org/basics/usagewithreact}{Redux-Saga}}
    +{\href{https://rnfirebase.io/}{RNFirebase}}}
    {
      \begin{projectitems} % Description(s) bullet points
        \item {{\href{http://doer.com.bd}{\textbf{DoerPay - }}}
        Currently under development, aggregated payment solution app.}
        \item {{\href{http://www.alarmlock.com/news/architech-bluetooth/}{\textbf{iLock - }}}
        Currently under development, NAPCO's Bluetooth LE solution app in React Native.}  
      \end{projectitems}
    }
%---------------------------------------------------------
\end{projectentries}
